Writing Trash Bin

### 2024-03-01 paper.qmd
added notes and adjusted some bits

> Edit note: this section is untouched since the confirmation. Might need a rewrite

@@

- @Boone2018

- @wu2023rational attempted to remedy this issue caused by designing a "rational agent benchmark" such that participants in an experiment are compared to a rational agent. This suggestion is an insufficient band-aid solution that is built upon the same invalid assumptions as the rest of the literature, and simply digs the field deeper into these problems, rather than solve them.

- @wu2023rational almost seems to recognise the problem of decision making experiments with payment schemes or correct/incorrect answers, but instead of understanding this boils these tasks down to value extraction, they suggest participants should be compared to a "rational agent". This rational agent acts as a benchmark, in the same way a ground truth statistic does for value extraction experiments, except the authors don't seem to realise that is what they have done. This paper highlights many decision making tasks are simply a value extraction experiment without realising it, this paper included.

@@

@@

>>>>

> Edit note: this section is untouched since the confirmation. Might need a rewrite. should comment that visualisation helps us understand *how* our data is different.

@@

- @Ibrekk1987 asked participants for the "best estimate" which was provided in terms of most probable value (mode), the mean and the median, the "ground truth" statistic used was the mean, despite the "best estimate" largely depending on the loss function of the model and the methods used.

- @Ibrekk1987 used several displays of a probability density functions, since “formally equivalent representations are often not psychologically equivalent”.

- @Ibrekk1987 highlights that in the face of a vague question, participants will use the plot to decide what the authors mean. The authors take this as a

- @Boone2018 organised responses from participants by the approach they used and tried to account for participants prior beliefs (although the assessment of those beliefs used the word "likely" which is open to interpretation).

There is so little understanding of information in uncertainty graphics that participants are frequently provided with information that is insufficient to answer the question at all, an issue that is regularly missed by the experimenters. In order to test whether or not people incorrectly interpreted the cone of uncertainty that is used to communicate cone tasks, experimenters regularly do not give participants enough information to answer the questions [@Padilla2017; @Boone2018]. The cone of uncertainty provides a 95% confidence interval for the *eye* of a hurricane, which allows us to know *where the eye of the storm will likely go*, this does not, give us enough information to answer if the storm will *hit* a particular point, because this requires information about the size and intensity of the storm, *and* an assumption about whether or not the size and intensity will change over time. Since these experiments are often trying to *test* for common misreadings of the plot, such as only thinking the area inside the cone will be damaged or believing the cone represents size and the storm is getting bigger. The authors often fail to recognize that the exact information that has been witheld for testing is necessary for answering their questions, and considering that information is necessary to mark participants as correct or incorrect, it is hard to understand exactly how they evaluated the experiment participants. @Ibrekk1987 expected participants to calculate the mean using a pie chart that had numerical bins combined (e.g. segment one was 0-2 inches of snow, and segment two was 2-4 inches of snow) so it could not be done by calculation. The authors also expected participants to use a CDF to calculate the mean, which needs to be converted *back* into a PDF to do so mathematically, so it was unclear how participants were supposed to do this calculation visually unless they were to just make a blind guess. The authors interpreted this as the participants misinterpreting how the CDF works, not seeming to realise they gave them an impossible task.
In light of this, the main take away from these papers seems to be "if you do not give people the necessary information to answer a question, they will be unable to answer it", which does not seem interesting enough to justify several papers.

@@

There are also some interesting qualitative studies that take an investigative stance to the use of uncertainty in decision making rather than an evaluation stance. @Daradkeh2015 presented participants with ten investment alternatives and asked participants "from among available alternatives, which alternative do you prefer the most", and were asked to think aloud and consider the uncertainty in their decision making. This study was qualitative and rather than setting a "correct" answer that would have forced a value of risk on the participants, the experimenters goal was to observe and organise the methods people use when making decisions in the face of uncertainty. This study was an excellent example in a useful experimental design. They highlighted the specific aspects of uncertainty that participants typically considered, such as the range of outcomes that are above/below a certain threshold, minimum and maximum values, the risk of a loss, etc, and mapped where in the decision making process participants made these considerations.

@@

# Conclusion
In this paper we have highlighted a series of misunderstandings, confusions, and methodical errors in the uncertainty literature.

Many of these issues are not problems in isolation, so long as the authors themselves are aware of it and state these assumptions in their papers. Our problem with this body is work is that the authors themselves seem to be oblivious to this vast array of problems, considering not a single one of the problems discussed here are mentioned explicitly in a single visualisation paper.

### 2024-03-01 writingdumpster.qmd
added notes and adjusted some bits

>>>>

- @Daradkeh2015 found that people tended to to make decisions on a small number of salient pieces of information rather than on systematic evaluations of the costs and benefits of choices.
- @Daradkeh2015 found that people tended to to make decisions on a small number of salient pieces of information rather than on systematic evaluations of the costs and benefits of choices.
@Daradkeh2015 found that people tended to ignore or give little weight probability information and instead focused on the severity of undersierable outcomes.
@Daradkeh2015 found that people tended to ignore or give little weight probability information and instead focused on the severity of undersierable outcomes.
- @wu2023rational attempted to remedy this issue caused by designing a "rational agent benchmark" such that participants in an experiment are compared to a rational agent. This suggestion is an insufficient band-aid solution that is built upon the same invalid assumptions as the rest of the literature, and simply digs the field deeper into these problems, rather than solve them. 
- @wu2023rational almost seems to recognise the problem of decision making experiments with payment schemes or correct/incorrect answers, but instead of understanding this boils these tasks down to value extraction, they suggest participants should be compared to a "rational agent". This rational agent acts as a benchmark, in the same way a ground truth statistic does for value extraction experiments, except the authors don't seem to realise that is what they have done. This paper highlights many decision making tasks are simply a value extraction experiment without realising it, this paper included.
